; extraction_mod_config.ltx
; Items listed in [keep_on_death] remain in the player's inventory when they
; die. All other items are transferred to the stash at the death location.
;
; Add any item section name as a key. The value is ignored -- presence is
; all that matters.

[keep_on_death]
device_pda_1        = true   ; player PDA tier 1 (starting PDA)
device_pda_2        = true   ; player PDA tier 2 (crafted)
device_pda_3        = true   ; player PDA tier 3 (crafted)
device_flashlight   = true   ; torch / flashlight
wpn_knife           = true   ; combat knife
wpn_knife2          = true   ; hunting knife
wpn_knife3          = true   ; machete
wpn_knife4          = true   ; cleaver
wpn_knife5          = true   ; kukri
wpn_axe             = true   ; fire axe
matches             = true   ; matches
box_matches         = true   ; box of matches

; [stash_npc_looting] -- optional simulation: death stashes lose random items
; over in-game time. When a stash is emptied it is removed from the world and
; its PDA marker cleared.
; When MCM is not installed, `enabled` turns the feature on. With MCM, use the
; MCM checkbox instead (this value is ignored if MCM has ever stored a value).
[stash_npc_looting]
enabled             = false
; Hours between loot pulses when MCM is absent or the MCM field is empty / invalid.
; With MCM installed, use Mod Configuration Menu → Extraction Mod → text field.
interval_game_hours = 12   ; 0 = disables in-game-time loot pulses entirely
; Decimals are allowed (e.g. 0.5 = every 30 in-game minutes).
; Chance (0..100) that each tracked stash loses one random item on a pulse.
; Rolled independently per stash every interval.
delete_chance_percent = 100
